working title Compatibility system and stigma size are the main predictors of heterospecific pollen effect

### 2019-03-04 Manuscript_draft/Manuscript_draft.Rmd
edits

\newpage
```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.width=6,fig.height=5, fig.cap="A"}
library(ape)
library(phytools)
pollen_tree=read.tree("Data/pollen_tree.nwk")
plot(pollen_tree)
add.scale.bar(x=0, y=1, length = 0.01)
```

>>>>

\newpage
```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, out.width='100%', fig.cap="A"}
knitr::include_graphics('images/phylo_image.png')
```
